Treefelling_Sylvain's version

### 2021-08-04 R/Treefelling_Sylvain's version.Rmd
get_geometry and import functions not package

  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], Foot[2] + dat$TreeHeight[1]),
                                    c(Foot[1] - TrailPt[1], Foot[2] -TrailPt[2]), degree = TRUE))

@@

ggplot() +
  # geom_sf(data = Foot) +
  # geom_sf(data = TrailPt) +
  geom_sf(data = FellingTrees)
```

@@

st_tree(SelectedTrees[1,],
        ScndTrail = ScndTrail,
        MainTrail = MainTrail,
        fuel = "2", directionalfelling ="2",
        advancedloggingparameters = loggingparameters())$A

FellingTrees <- inventory %>%
  group_by(idTree) %>% 
  mutate(geometry =
           ifelse(!is.na(TreeFellingOrientationSuccess),
                  "A", "B"))

FellingTrees <- inventory %>%
  group_by(idTree) %>% 
  do(geometry =
       ifelse(!is.na(.$TreeFellingOrientationSuccess),
              tolower("A"), "B"))

@@

?sf
st_as_text(poly$geometry)

felttrees <- inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>%

       st_tree(.,
               ScndTrail = ScndTrail,
               MainTrail = MainTrail,
               fuel = "2", directionalfelling = "2",
               advancedloggingparameters = loggingparameters())$A %>% 
       st_as_text())  # as text to easy join with a non spacial table
  # unnest(treepolygon) # display the small dataframe in the big dataframe in one

@@

get_treepolygon <- function(inventory){ # function from text (wkt) to sf
       st_as_text()) %>% 
  unnest(treepolygon)

@@

get_treepolygon <- function(inventory){
  inventory %>% 
    filter(!is.na(treepolygon)) %>%
    st_as_sf(wkt = "treepolygon")
}

ggplot() +
  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) + # all the individuals of the plot
  geom_sf(data = get_treepolygon(inventory), fill = "red") # trees polygons

st_intersection( # trees under the fallen trees
  get_treepolygon(inventory),
  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
  geom_sf(data = get_treepolygon(inventory2), fill = "red")

st_intersection(
  get_treepolygon(inventory2),
  st_as_sf(inventory, coords = c("Xutm", "Yutm"))
) %>% 
  ggplot() +
  geom_sf()
```

>>>>

  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                    c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))

@@

library(ggplot2)
ggplot() +
  geom_sf(data = st_union(Trunk, Crown), colour = "red") +
  geom_sf(data = Foot) +
  geom_sf(data = Trail) +
  geom_sf(data = TrailPt) +
  geom_sf(data = NearestPoints) +
  geom_sf(data = A)+
  geom_sf(data = B)

@@

@@

st_as_text(poly$geometry)

felttrees <- inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
  st_tree(.,
          ScndTrail = ScndTrail,
          MainTrail = MainTrail,
          fuel = "2", directionalfelling = "2",
          advancedloggingparameters = loggingparameters())$A %>% 
  st_as_text()  # as text to easy join with a non spacial table
# unnest(treepolygon) # display the small dataframe in the big dataframe in one

@@

get_geometry <- function(inventory){ # function from text (wkt) to sf
  st_as_text() %>% 
    unnest(treepolygon)
}

@@

get_geometry <- function(inventory){
  inventory %>% 
    filter(!is.na(treepolygon)) %>%
    st_as_sf(wkt = "treepolygon")
}

ggplot() +
  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) + # all the individuals of the plot
  geom_sf(data = get_geometry(inventory), fill = "red") # trees polygons

st_intersection( # trees under the fallen trees
  get_geometry(inventory),
  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
    geom_sf(data = get_geometry(inventory2), fill = "red"))

st_intersection(
  get_geometry(inventory2),
  st_as_sf(inventory, coords = c("Xutm", "Yutm"))
) %>% 
  ggplot() +
  geom_sf()
```
```{r}
inventory <- successfail(
  inventory,
  fuel = "2", directionalfelling = "2",
  advancedloggingparameters = loggingparameters())

# Treefelling
felttrees <- inventory %>%
  filter(!is.na(TreeFellingOrientationSuccess)) %>%
  group_by(idTree) %>% # for each tree
  do(TreePolygon = # inform geometry. # Filling a column from a function whose input is a table
       st_tree(.,
               fuel = "2", directionalfelling = "2",
               MainTrail = MainTrail, ScndTrail = ScndTrail,
               advancedloggingparameters = loggingparameters())$A %>%
       st_as_text()) %>% # as text to easy join with a non spacial table
  tidyr::unnest(TreePolygon) # here to pass from list to character

inventory <- left_join(inventory, felttrees, by = "idTree") # join spatial filtered inventory and non spatial complete inventory
